Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-01 MDPI_submission.Rmd
Commit 2023-12-01 14:14

<!-- ### Data selection -->
Due to the significant measurement uncertainty when the Sun is near the horizon, we have excluded all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$.
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with azimuth angle between
$`r FIBais_Az_1`^\circ$ and $`r FIBais_Az_2`^\circ$ with SZA greater than $`r 90 -  FIBais_Elev`^\circ$.
On the latter instances, Sun is systematically not visible from the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all one-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a time series of satellite TSI observations.
The TSI data we used are part of the "NOAA Climate Data Record of Total Solar Irradiance" dataset [@Coddington2005].
The initial daily values of this dataset were interpolated to match the time step of our measurements.
In the final dataset
<!-- $`r SDR_N_All`$ -->
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$
of the 1-min data were identified as under clear-sky conditions and
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
as under cloud-sky conditions.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->

>>>>

<!-- ### Data selection -->
Due to the significant measurement uncertainty when the Sun is near the horizon, we have excluded all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$.
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with azimuth angle between
$`r FIBais_Az_1`^\circ$ and $`r FIBais_Az_2`^\circ$ with SZA greater than $`r 90 -  FIBais_Elev`^\circ$.
On the latter instances, Sun is systematically not visible from the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all one-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a time series of satellite TSI observations.
The TSI data we used are part of the "NOAA Climate Data Record of Total Solar Irradiance" dataset [@Coddington2005].
The initial daily values of this dataset were interpolated to match the time step of our measurements.
In the final dataset
<!-- $`r SDR_N_All`$ -->
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$
of the 1-minute data were identified as under clear-sky conditions and
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
as under cloud-sky conditions.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->
